Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours

### 2024-09-24 outputs/paper/paper.qmd
constructed the backbone of the paper, started working on the intro seciton

# Introduction

@@

# Data {#sec-data}

## TTC Bus Delay

@@

## TTC Streetcar Delay

@@

## TTC Subway Delay

### Delay Code
```{r}
#| label: tbl-subway-code
#| tbl-cap: Sample of TTC Subway Delay Code
#| echo: false
#| message: false

@@

### Delay Data
```{r}
#| label: tbl-subway-delay
#| tbl-cap: Sample of Cleaned TTC Subway Delay Dataset
#| echo: false
#| message: false

@@

## TTC Delay Comparision

>>>>

# Introduction
1) broader context to motivate
- Public transportation is an important part of urban life, it is responsible for transporting millions of people around the city everyday. Choosing the correct TTC service offers a more stable timetable for office workers, student, and the elderly alike.

2) some detail about what the paper is about; a clear gap that needs to be filled
- TTC data has been publicly available since 2014, this paper seeks to use these open-sourced data to visualize how each type of TTC service performs through their delay time. 
- TTC bus, streetcar, and subway delay data are all collected through @OpenDataToronto data portal.

3) what was done
- TTC bus, streetcar, and subway delay data in 2023 were extracted and compared to determine the TTC service type that offers the least amount of delay during weekday rush-hours.

4) what was found
- TTC subways has a history of offering the least average delay in 2023.

5) why it is important
- assist readers in choosing between different TTC services given that the distance between their residence and different types of TTC stations are the same.

@@

# Data {#sec-data}
Where the data comes from

which datasets where chosen

why choose 2023

## TTC Bus Delay {#sec-data-bus}
source of data (brief)
structure of data & important attributes
why are these attributes kept for analysis (measurement)

@@

## TTC Streetcar Delay {#sec-data-streetcar}
source of data (brief)
structure of data & important attributes
why are these attributes kept for analysis (measurement)

@@

## TTC Subway Delay {#sec-data-subway}
source of data (brief)

### Delay Code {#sec-data-code}
purpose of extra dataset
how it is related to subway_delay
```{r}
#| label: tbl-subway-code
#| tbl-cap: Sample of TTC Subway Delay Code
#| echo: false
#| message: false

@@

### Delay Data
structure of data & important attributes
why are these attributes kept for analysis (measurement)
mention "code" column
```{r}
#| label: tbl-subway-delay
#| tbl-cap: Sample of Cleaned TTC Subway Delay Dataset
#| echo: false
#| message: false

@@
